---
title: "Authentication and Billing reference guide for Seven Bridges API R Client"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: false
    theme: "flatly"
    highlight: "textmate"
    css: "sevenbridges.css"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Authentication and Billing reference guide for Seven Bridges API R Client}
  %\VignetteEncoding{UTF-8}
---

<a name="top"></a>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Authentication

Before you can interact with the API, you need to construct an `Auth` object 
which stores the following information:

- Your authentication token. This is used to authenticate your credentials 
with the API. Learn more about obtaining your authentication token on the 
[Seven Bridges Platform](https://docs.sevenbridges.com/v1.0/docs/get-your-authentication-token), 
[Cancer Genomics Cloud (CGC)](http://docs.cancergenomicscloud.org/v1.0/docs/get-your-authentication-token),
[BioData Catalyst (BDC)](https://sb-biodatacatalyst.readme.io/docs/get-your-authentication-token#find-your-authentication-token), and [CAVATICA](https://docs.cavatica.org/docs/get-your-authentication-token#your-authentication-token).

The approach for obtaining the authentication token also applies to the other 
Seven Bridges platforms.

- The path for the API (base URL).
- The name of the platform you are using. This is an optional field, as the base 
URL of the API ultimately decides where the API calls will be sent to. 
This field will only be blank when the URL was directly provided, and the 
platform name could not be inferred from that URL.

The general authentication logic for `Auth$new()` is as follows:

1. The package will use the direct authentication method if the `from` 
parameter is not specified explicitly or is specified as `from = "direct`.
2. The package will load the authentication information from environment 
variables when `from = "env"`, or user configuration file when `from = "file"`.

## Direct authentication

To use direct authentication, users need to specify one of `platform` or `url`,
with the corresponding `token`. Examples of direct authentication:

```{r}
# Direct authentication with setting platform parameter
a <- Auth$new(
  token = "<your_token>",
  platform = "aws-us"
)
```

The above will use the Seven Bridges Platform on AWS (US).

```{r}
# Direct authentication with setting url parameter
a <- Auth$new(
  token = "<your_token>",
  url = "https://api.sb.biodatacatalyst.nhlbi.nih.gov/v2/"
)
```

The above will use the specified `url` as the base URL for the API calls. 
In this example, the `url` points to BioData Catalyst powered by Seven Bridges.

```{r}
# Direct authentication on default aws-us platform
a <- Auth$new(token = "<your_token>")
```

The above will use the Seven Bridges Platform on AWS since neither `platform` 
nor `url` were explicitly specified.

***Note:*** `platform` and `url` should not be specified at the same time.

<div align="right"><a href="#top">top</a></div>

## Authentication via system environment variables

The R API client supports reading authentication information stored in
system environment variables.

To set the two environment variables in your system, use the function 
`sbg_set_env()`. For example:

```{r}
# Set environment variables
sevenbridges2:::sbg_set_env(
  url = "https://cgc-api.sbgenomics.com/v2",
  token = "<your_token>"
)
```

See if the environment variables are correctly set:

```{r}
# Check environment variables
sevenbridges2:::sbg_get_env("SB_API_ENDPOINT")
## "https://cgc-api.sbgenomics.com/v2"

sevenbridges2:::sbg_get_env("SB_AUTH_TOKEN")
## "<your_token>"
```

Now you can create the `Auth` object:

```{r}
# Authenticate using environment variables
a <- Auth$new(from = "env")
```

To unset the two environment variables:

```{r}
# Unset environment variables
Sys.unsetenv("SB_API_ENDPOINT")
Sys.unsetenv("SB_AUTH_TOKEN")
```

If you need to be logged into multiple accounts at the same time it is 
essential that you provide environment variables for each of the accounts. 
Of course, these variables must have different names.

If you do not have pre-set environment variables, you can create them in the 
following way:

```{r}
# Set environment variables for the first account
sevenbridges2:::sbg_set_env(
  url = "https://api.sbgenomics.com/v2",
  token = "<your_token>",
  sysenv_url_name = "account_1_url",
  sysenv_token_name = "account_1_token"
)

# Set environment variables for the second account
sevenbridges2:::sbg_set_env(
  url = "https://api.sb.biodatacatalyst.nhlbi.nih.gov/v2/",
  token = "<your_token>",
  sysenv_url_name = "account_2_url",
  sysenv_token_name = "account_2_token"
)
```

Now you are ready to create an authentication object for these two accounts:

```{r}
# Authenticate using the first account
a <- sevenbridges2::Auth$new(
  from = "env",
  sysenv_url = "account_1_url",
  sysenv_token = "account_1_token"
)

# Authenticate using the second account
b <- sevenbridges2::Auth$new(
  from = "env",
  sysenv_url = "account_2_url",
  sysenv_token = "account_2_token"
)
```

<div align="right"><a href="#top">top</a></div>

## Authentication via user configuration file

You can create an ini-like file named `credentials` under the folder 
`$HOME/.sevenbridges/` and maintain your credentials for multiple accounts 
across various Seven Bridges environments. An example:

```
[aws-us-rfranklin]
api_endpoint = https://api.sbgenomics.com/v2
auth_token = token_for_this_user

# This is a comment:
# another user on the same platform
[aws-us-rosalind-franklin]
api_endpoint = https://api.sbgenomics.com/v2
auth_token = token_for_this_user

[default]
api_endpoint = https://cgc-api.sbgenomics.com/v2
auth_token = token_for_this_user

[bdc]
api_endpoint = https://api.sb.biodatacatalyst.nhlbi.nih.gov/v2/
auth_token = token_for_this_user
```

Please make sure to have two fields named **exactly** as `api_endpoint` 
and `auth_token` under each profile.

To load the default profile (named `[default]`) from the default user
configuration file (`$HOME/.sevenbridges/credentials`), please use:

```{r}
# Authenticate using file configuration
a <- Auth$new(from = "file")
```

To load the user profile `aws-us-<username>` from this configuration file,
change the `profile_name`:

```{r}
# Authenticate using file configuration and specific profile
a <- Auth$new(from = "file", profile_name = "aws-us-<username>")
```

To use a user configuration file from other locations (not recommended),
please specify the file path using the argument `config_file`. For example:

```{r}
# Authenticate using specific file configuration on custom path
a <- Auth$new(
  from = "file", config_file = "~/sevenbridges.cfg",
  profile_name = "aws-us-<username>"
)
```

***Note:*** If you edited the `credentials` file, please use `Auth$new()` to 
re-authenticate.

<div align="right"><a href="#top">top</a></div>

# API general information

## Advance Access Features

Similar to `offset` and `limit`, every API call accepts an argument named
`advance_access`. This argument was first introduced in August 2017 and 
controls if a special field in the HTTP request header will be sent, 
which can enable access to the "Advance Access" features in the Seven Bridges 
API. 

In addition to modifying each API call that uses Advance Access features, 
the option can also be set globally at the beginning of your API script. 
This offers a one-button switch for users who want to experiment with 
Advance Access features. The option is disabled by default:

```{r}
# Load package and check advance access option
library("sevenbridges2")
getOption("sevenbridges2")$advance_access
```

```
## [1] FALSE
```
For example, if we try to use the Markers API to list markers available 
on a BAM file with the `advance_access` option disabled, it will return an 
error message:

```{r}
# Authenticate first
a <- Auth$new(token = "<your_token>", platform = "aws-us")

# Try to send request to list markers
req <- a$api(
  path = "genome/markers?file={bam_file_id}",
  method = "GET"
)
```

```
## !HTTP Status 400: Advance access feature needs X-SBG-Advance-Access: advance header.
```

To enable the Advance Access features, one can use

```{r}
# Enable advance access option
opt <- getOption("sevenbridges2")
opt$advance_access <- TRUE
options(sevenbridges2 = opt)
```

at the beginning of their scripts. Let's check if the option has been enabled:

```{r}
# Check advance_access option again
getOption("sevenbridges2")$advance_access
```

```
## [1] TRUE
```

Send the API call again:

```{r}
# Send request again to list markers
req <- a$api(
  path = "genome/markers?file={bam_file_id}",
  method = "GET"
)
```

The information on the markers available on that BAM file will be returned:

```{r}
# Read content
httr::content(req)
```

```
$href
[1] "https://api.sbgenomics.com/v2/genome/markers?file={bam_file_id}&offset=0&limit=50"

$items
$items[[1]]
$items[[1]]$href
[1] "https://api.sbgenomics.com/v2/genome/markers/{bam_file_id}"

$items[[1]]$id
[1] "{bam_file_id}"

$items[[1]]$name
[1] "Marker Title"

$items[[2]]
$items[[2]]$href
[1] "https://api.sbgenomics.com/v2/genome/markers/{bam_file_id}"

$items[[2]]$id
[1] "{bam_file_id}"

$items[[2]]$name
[1] "Marker Title"

$links
list()
```

<div align="right"><a href="#top">top</a></div>

## Query Parameter `fields`

All API calls take the optional query parameter `fields`. This parameter 
enables you to specify the fields you want to be returned when listing resources
(e.g., all your projects) or getting details of a specific resource 
(e.g., a given project).

The `fields` parameter can be used in the following ways:

1. No `fields` parameter specified: returns **all fields** for each 
resource returned (TBD for Apps).

2. The `fields` parameter can be set to a list of fields: for example, 
to return a field's id, name and size for files in a project, you may issue 
the call `p$list_files(fields = c("id" ,"name", "size"))`.

3. The `fields` parameter can be used to exclude a specific file: if you wish to 
omit a certain field from the response, do so using the `fields` parameter with 
the prefix `!`. For example, to get the details of a file without listing its 
metadata, issue a call `p$list_files(fields = "!metadata")` or to exclude 
multiple fields `p$list_files(fields = c("!metadata", "!tags"))`.
The entire metadata and tags fields will be removed from the response.

4. The `fields` parameter can be used to include or omit certain nested fields, 
in the same way as listed in 2 and 3 above: for example, you can use 
`metadata.sample_id` or `origin.task` for files.

5. Negations and nesting can be combined freely, so, for example, you can issue 
`p$list_files(fields = c("id", "name", "size", "!metadata.library", "!origin"))`.

<div align="right"><a href="#top">top</a></div>

## Rate Limits

This call returns information about your current rate limit.
This is the number of API calls you can make in one hour.

```{r}
# Get rate limit info
a$rate_limit()
```

It shows information about the remaining number of API calls to make in one
hour, along with time when the rate limit resets, and the total and remaining
number of instances available to the user.

```
── Rate limit ──────────────────────────────────────────────────────────────
• rate
  • limit: 1000
  • remaining: 998
  • reset: 2023-11-27 14:24:38 CET
• instance
  • limit: 25
  • remaining: 25
```

<div align="right"><a href="#top">top</a></div>

## General API error handlers

We should also mention that there are 3 types of general API errors that are 
handled by the client `sevenbridges2` package:

- **Rate limit sleeper** which pauses the execution of any API 
call if rate limit is breached. The execution will automatically continue 
when the required break time expires,
- **Maintenance sleeper** which pauses the execution if Seven Bridges API is 
under maintenance and
- **General error sleeper** which pauses the execution if response status code 
is equal or larger than 500 (if some server error occurred). 

# List All API Calls

Users are able to preview all main resource paths that exist on the public
Seven Bridges API. 
If you do not pass any parameters to `api()` from the `Auth` object, it will 
list all API calls. Any parameters you provide will be passed to the `api()` 
function, but you do not have to pass your input token and path once more 
since the `Auth` object already handles this information. 
The following call from the `Auth` object will check the response as well.

```{r}
# List all API paths
a$api()
```

<div align="right"><a href="#top">top</a></div>


# Users

This call will return a successful response of the currently authenticated user, 
while if you have some advanced privileges as an Enterprise user, you can 
fetch information about other users when specifying their usernames. 

If you did not provide a username, it will show your user information.

```{r}
# Return your information
a$user()

# Return user RFranklin's information
a$user(username = "RFranklin")
```

<div align="right"><a href="#top">top</a></div>

# Billing Groups and Invoices

## Billing groups

Billing operations are grouped under the `Billing_groups` R6 Resource class and 
from here you can query all billing groups or fetch a single one by its id. 

When you fetch a single billing group it will be an object of the `Billing` 
class.

```{r}
# Get specific billing group
my_billing_group <- a$billing_groups$get(id = "<billing_group_id>")

# You can still print the billing group info by calling the print method
my_billing_group$print()
```

You can also get detailed information for a specific billing group. 
The following options are available to you:

- analysis breakdown
- storage breakdown
- egress breakdown.

To get an analysis breakdown for a billing group which contains information 
on both the tasks and Data Studio analyses, call:

```{r}
# Get analysis breakdown
my_billing_group$analysis_breakdown()
```

To get storage breakdown for a billing group, call:

```{r}
# Get storage breakdown
my_billing_group$storage_breakdown()
```

Finally, you may want to get egress breakdown for a billing group:

```{r}
# Get egress breakdown
my_billing_group$egress_breakdown()
```

If something changes in the billing group, you can refresh your `Billing`
object by reloading it with:

```{r}
# Reload Billing objcet
my_billing_group$reload()
```

<div align="right"><a href="#top">top</a></div>

## Invoices

The same logic applies for the invoices - the operations available for invoices 
are grouped under the `Invoices` class and from here you can query or fetch a 
single invoice with resource operations `query()` and `get()`.

Listing all invoices doesn't require any arguments to set, while if you would
like to list invoices of specific billing group, set the `billing_group`
parameter to the desired value. 

```{r}
# List invoices of specific billing group
invoices_bg <- a$invoices$query(billing_group = "<billing_group_id>")

# Print invoices
invoices_bg
```

Keep in mind that the result is `Collection` object which stores the returned
items in the `items` field.

To retrieve information about a single invoice, including the costs for 
analysis and storage, and the invoice period, you can use the `get()` method 
with the id parameter set to the ID of the invoice you are querying.

```{r}
# Get specific invoice by ID
invoice <- a$invoices$get(id = "<invoice_id>")

# Print
invoice
```

```
── Invoice info ──────────────────────────────────────────────────────────────────────────────────────────────────────────────────────────────────────
• approval_date: 2022-02-01T00:00:00Z
• pending: FALSE
• invoice_id: <your_invoice_id>
• href: https://api.sbgenomics.com/v2/billing/invoices/<your_invoice_id>
• invoice_period
  • from: 2022-01-01T00:00:00Z
  • to: 2022-01-31T23:59:59Z
• analysis_costs
  • currency: USD
  • amount: 101.77
• storage_costs
  • currency: USD
  • amount: 256.11
• total
  • currency: USD
  • amount: 357.88
```

If something changes, you can always refresh your local `Invoice` object by 
reloading it with:

```{r}
# Reload Invoice object
invoice$reload()
```

<div align="right"><a href="#top">top</a></div>

# Send a feedback item

Lastly, to send feedback to Velsera via the API, you can use the `Auth` class 
method `send_feedback()`. 
There are three feedback types available: `"idea"`, `"thought"`, or `"problem"`. 
You can send one feedback item per minute.

```{r}
# Send feedback
a$send_feedback(
  "This is a test for sending feedback via API. Please ignore this message.",
  type = "thought"
)
```

<div align="right"><a href="#top">top</a></div>
