---
title: "Enterprise actions reference guide for Seven Bridges API R Client"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: false
    theme: "flatly"
    highlight: "textmate"
    css: "sevenbridges.css"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Managing Divisions with Seven Bridges API R Client}
  %\VignetteEncoding{UTF-8}
---


<a name="top"></a>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Managing Divisions

Enterprise access to the Platform is available on demand and allows companies
or organizations to mimic their internal structure and hierarchy on the Seven
Bridges Platform, thus facilitating simpler and more efficient collaboration.

Enterprise accounts are granted to users through their organizations. The
organization associated with the Enterprise account may create user groups
(`Divisions` and `Teams`) composed of Enterprise account holders, which are
used to enable collaboration between members of the organization.

A `Division` on the Platform is a subgroup of users within an `Enterprise`. Use
the `Division` entity to replicate the structure and hierarchy of an
organization, such as departmental groups on the Platform. `Enterprise`
administrators create `Divisions`, but they can assign `Division`
administrators to manage them.

A `Team` is a subgroup within a `Division`. Division administrators can create
`Teams` to simplify adding multiple members to a project at once. A single
`Division` member can belong to multiple `Teams`.

Division related operations can be accessed through the `divisions` path
from the `Auth` object.

When fetching a single division, it is represented as a `Division` object,
which contains the following information:

- `id`: Division ID
- `name`: Division name

The division object also has additional methods that can be executed directly
on it, such as: `TO BE ADDED`



## List all your divisions

The following call returns a Collection with a list of all divisions you are a
member of. Each division ID, name and URL on the Seven Bridges Platform will be
returned.

```{r}
# Authenticate (division authentication token is required)
a <- Auth$new(platform = "aws-us", token = "<your-token>")

# Query all divisions of which you are a member
a$divisions$query()
```


## Get details of a division

The following call returns the details of a specified division.

```{r}
# Retrieve details of a specified division
a$divisions$get(id = "division-id")
```


## List all your teams in a division

To retrieve a list of all teams in a division that you are a member of, use the
`list_teams()` method of a `Division` object. This method returns a
`Collection` of `Team` objects, each containing the team's ID and name.

If you want to list all teams within the division, regardless of whether you
are a member, set the `list_all` parameter to `TRUE`.

```{r}
# Retrieve details of a specified division
my_division <- a$divisions$get(id = "division-id")

# List division teams you are a member of
my_division$list_teams()

# List all teams in the division, including those you are not a member of
my_division$list_teams(list_all = TRUE)
```


## List members of a division

To retrieve a list of all members in a division, use the `list_members()`
method of a `Division` object. This method returns a `Collection` of `User`
objects, each containing user details.

If you want to filter members by role, you can specify the `role` parameter. 
The supported roles are `"ADMIN"`, `"MEMBER"`, and `"EXTERNAL_COLLABORATOR"`.
The default value for this parameter is `NULL`, meaning that if `role` is not
provided, members of all roles will be included in the results.

```{r}
# Retrieve details of a specific division
my_division <- a$divisions$get(id = "division-id")

# List all members in the division
my_division$list_members()

# List only members with the "ADMIN" role
my_division$list_members(role = "ADMIN")
```


## Remove a member from a division

To remove a member from a division, use the `remove_member()` method of a
`Division` object. This action revokes the user's membership in the division
but does not delete their Platform account.

Only users with the `ADMIN` role in the division have permission to remove
members. If a user without `ADMIN` privileges attempts to perform this action,
an error will be raised.

The user parameter accepts either a username (formatted as
`"division-name/username"`) or a `User` object.

```{r}
# Retrieve details of a specific division
my_division <- a$divisions$get(id = "division-id")

# Remove a member using their username
my_division$remove_member(user = "division-name/username")

# Remove a member using a User object
members <- my_division$list_members(role = "MEMBER")
member_to_remove <- members$items[[1]]
my_division$remove_member(user = member_to_remove)
```
