---
title: "Managing Divisions with Seven Bridges API R Client"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: false
    theme: "flatly"
    highlight: "textmate"
    css: "sevenbridges.css"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Managing Divisions with Seven Bridges API R Client}
  %\VignetteEncoding{UTF-8}
---


<a name="top"></a>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Managing Divisions

Enterprise access to the Platform is available on demand and allows companies
or organizations to mimic their internal structure and hierarchy on the Seven
Bridges Platform, thus facilitating simpler and more efficient collaboration.

Enterprise accounts are granted to users through their organizations. The
organization associated with the Enterprise account may create user groups
(`Divisions` and `Teams`) composed of Enterprise account holders, which are
used to enable collaboration between members of the organization.

A `Division` on the Platform is a subgroup of users within an `Enterprise`. Use
the `Division` entity to replicate the structure and hierarchy of an
organization, such as departmental groups on the Platform. `Enterprise`
administrators create `Divisions`, but they can assign `Division`
administrators to manage them.

A `Team` is a subgroup within a `Division`. Division administrators can create
`Teams` to simplify adding multiple members to a project at once. A single
`Division` member can belong to multiple `Teams`.

Division related operations can be accessed through the `divisions` path
from the `Auth` object.

When fetching a single division, it is represented as a `Division` object,
which contains the following information:

- `id`: Division ID
- `name`: Division name

The division object also has additional methods that can be executed directly
on it, such as: `TO BE ADDED`



## List all your divisions

The following call returns a Collection with a list of all divisions you are a
member of. Each division ID, name and URL on the Seven Bridges Platform will be
returned.

```{r}
# Authenticate (division authentication token is required)
a <- Auth$new(platform = "aws-us", token = "<your-token>")

# Query all divisions of which you are a member
a$divisions$list_all_divisions()
```


## Get details of a division

The following call returns the details of a specified division.
```{r}
# List all your divisions
a$divisions$get_division_details(division_id = "division-id")
```
